The Wolf in Sheep's Clothing:\\ Subversive Adversarial Agent Identification

### 2016-08-13 article.tex
added changes and changed structure a bit

Now that we have a defined state we must gather the state from a combination of sensor data and information obtained from the robot. We use a particle filter for this purpose which we initialize to cover the full area of interest. If an initial position is provided a particle is given that claimed position, but all others are kept in their random position to accommodate for a false given position.

We obtain the average of the particles  which is utilized in order to obtain an approximate point nearest to some neighbors on two maps: a compromised map and an uncompromised map. Both maps are comprised of state points along the path planned that are considered compromised or uncompromised as illustrated in figure~\ref{fig:compmaps}.

A KD tree is used on both maps to find the closest approximate points to each mean found. The few particles gathered by this process are used, by the compromised and uncompromised maps, to form probability density function (PDF) by means of a Kernel density estimation (KDE). This distribution is used to obtain the probability the mean of the particle filter approximation falls within each map. The product of these two probability biases the input to the next iteration to the Bayes equation \ref{fig:Bayes} where b = behavior of the robot, s = state of the robot and c = the probability the robot is compromised.

\begin{equation}
 \beta el =\frac {(P(b,s|c)P(c)} {(P(b,s|c)P(c) + 
 P(b,s|c' )P(c' ))} 
 \label{fig:Bayes}
\end{equation}

This implementation provides a way a way for the change in behavior, that is from uncompromised to compromised or vice versa, to impact the current belief.

@@

@@

\subsection{Prediction}

>>>>

@@

Now that we have a defined state we must gather the state from a combination of sensor data and information obtained from the robot. We use a particle filter for this purpose which we initialize as to cover the full state space. Particle filters are useful as they represent the posterior belief by a set of random state samples drawn from its posterior\cite{Thrun2002Probabilistic}. If an initial state is provided a particle is placed that claimed state, but all others are kept in their random position to accommodate for a possible false given position.

We obtain the average of the particles  which is utilized in order to obtain an approximate point nearest to some neighbors on two maps: a compromised map and an uncompromised map. Both maps are comprised of state points along the path planned that are considered compromised or uncompromised as illustrated in ~\autoref{fig:compmaps}.

A KD tree is used on both maps to find the closest approximate points to each mean found. The few particles gathered by this process are used, by the compromised and uncompromised maps, to form Probability Density Function (PDF) by means of a Kernel Density Estimation (KDE). 
\begin{equation}
 P(c,b|s) =\frac {(P(b,s|c)P(c)} {(P(b,s|c)P(c) + 
 P(b,s|c' )P(c' ))} 
 \label{fig:Bayes}
\end{equation}
This distribution is used to obtain the probability the mean of the particle filter approximation falls within each map. The product of these two probability biases the input to the next iteration to the Bayes equation \ref{fig:Bayes} where b = behavior of the robot, s = state of the robot and c = the probability the robot is compromised \cite{Thrun2002Probabilistic}. This implementation provides a way for the change in behavior to impact the current belief.

@@
